### 2014-04-01 Docs/flowchart/flowchart.tex
finish documenting how we handle the delta_gamma1_term

\item In {\bf Step 7}, we now include the $\delta \Gamma_1$ term in the righthand
side for the constraint by solving:
\begin{equation}
\nabla \cdot \left(\beta_0^{\nph,\star} \uadvtwo\right) =
\beta_0^{\nph,\star}\left( S^{\nph,\star} - \overline{S^{\nph,\star}} +
   \frac{\Gamma_1^{n+1,\star} - \overline{\Gamma_1^{n+1,\star}}} 
         {{\overline{\Gamma_1^{n+1,\star}}}^2} \frac{1}{p_0^n} 
         (\psi^{\nph,\star} + \Ubt^n \cdotb \nablab p_0^n)
\right)
\end{equation}
We note that this includes the average of the correction term as shown
in Eq.~\ref{eq:constraint_with_delta_gamma} because we modified
$\bar{S}$ to include this already.
\end{itemize}

>>>>

\item In {\bf Step 7}, we now include the $\delta \Gamma_1$ term in the righthand
side for the constraint by solving:
\begin{equation}
\nabla \cdot \left(\beta_0^{\nph,\star} \uadvtwo\right) =
\beta_0^{\nph,\star}\left( S^{\nph,\star} - \overline{S^{\nph,\star}} +
   \frac{\Gamma_1^{n+1,\star} - \overline{\Gamma_1^{n+1,\star}}} 
         {{\overline{\Gamma_1^{n+1,\star}}}^2} \frac{1}{p_0^n} 
         (\psi^{\nph,\star} + \Ubt^n \cdotb \nablab p_0^n)
\right)
\end{equation}
We note that this includes the average of the correction term as shown
in Eq.~\ref{eq:constraint_with_delta_gamma} because we modified
$\bar{S}$ to include this already.

\item In {\bf Step 10}, we do a construction much like that done in {\bf Step 6},
but with the time-centerings of some of the quantities changed.
First we construct:
\begin{equation}
\frac{\delta \Gamma_1}{\Gamma_1^2 p_0} \Ubt \cdotb \nablab p_0 \approx
   \frac{\Gamma_1^{n+1} - \overline{\Gamma_1^{n+1}}}
         {{\overline{\Gamma_1^{n+1}}}^2} \frac{1}{p_0^{n+1}} \Ubt^n \cdotb \nablab p_0^{n+1}
\end{equation}
Then we call {\bf average} to construct the lateral average of this
\begin{equation}
\overline{\frac{\delta \Gamma_1}{\Gamma_1^2 p_0} \Ubt \cdotb \nablab p_0} = 
   \mathbf{Avg} \left (\frac{\Gamma_1^{n+1} - \overline{\Gamma_1^{n+1}}}
         {{\overline{\Gamma_1^{n+1}}}^2} \frac{1}{p_0^{n+1}} \Ubt^n \cdotb \nablab p_0^{n+1} \right )
\end{equation}

Again we modify $\overline{S}$ to include this average:
\begin{equation}
\overline{S^{n+1}} \leftarrow \overline{S^{n+1}} + 
   \overline{\frac{\delta \Gamma_1}{\Gamma_1^2 p_0} \Ubt \cdotb \nablab p_0} 
\end{equation}

\item In {\bf Step 11}, we modify the source of the constraint to include the
$\delta \Gamma_1$ information.  In particular, we solve:
\begin{equation}
\nabla \cdot \left(\beta_0^{\nph} \Ubt^{n+1} \right) 
= \beta_0^{\nph} \left(S^{n+1} - \overline{S^{n+1}} +
   \frac{\Gamma_1^{n+1} - \overline{\Gamma_1^{n+1}}} 
         {{\overline{\Gamma_1^{n+1}}}^2} \frac{1}{p_0^{n+1}}
         (\psi^{\nph} + \Ubt^n \cdotb \nablab p_0^{n+1})
\right)
\end{equation}
